Government through Patronage

### 2020-07-06 presentation/presentation_job_market.Rmd
improve file naming

path_figs <- "papers/paper_cp_2020/figs/"

@@

```{r out.width = '240px'}
include_graphics(
  'figs/plot_global_1.pdf'
)
```

@@

```{r out.width = '240px'}
include_graphics(
  'figs/plot_global_2.pdf'
)
```

@@

```{r, fig.cap= "Municipal variation in the quality of education (2015). Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores.", out.width = "180px"}
include_graphics(
  "figs/saeb_map.pdf"
)
```

@@

```{r fig.cap = "A decentralized system. Lower school education is primarily under the responsibility of municipalities."}
include_graphics(
  "figs/enrollment_dep.pdf"
)
```

@@

```{r staff, fig.cap = 'Municipal bureaucracies. Total number of bureaucrats and hiring/dismissal rates for bureaucratic staff over time. Disaggregated by department.'}
include_graphics(
  'figs/turnover_category.pdf'
)
```

@@

```{r, fig.cap= "Relative impact of bureaucratic turnover. Point estimates and confidence intervals retrieved from models with controls.", out.width = "210px"}
include_graphics(
  "figs/turnover_fit.pdf"
)
```

@@

```{r fig.cap = "Predicted and actual values for bureaucratic turnover. The line graph plots the predicted proportion of educational staff hired or firede. Circles' size is proportional to the number of observations contained in the data."}
include_graphics(
  "figs/plot_pred.pdf"
)
```

>>>>

path_figs <- "papers/paper_cp_2020/plots/"

@@

```{r out.width = '240px'}
include_graphics(
  'plots/plot_global_1.pdf'
)
```

@@

```{r out.width = '240px'}
include_graphics(
  'plots/plot_global_2.pdf'
)
```

@@

```{r, fig.cap= "Municipal variation in the quality of education (2015). Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores.", out.width = "180px"}
include_graphics(
  "plots/saeb_map.pdf"
)
```

@@

```{r fig.cap = "A decentralized system. Lower school education is primarily under the responsibility of municipalities."}
include_graphics(
  "plots/enrollment_dep.pdf"
)
```

@@

```{r staff, fig.cap = 'Municipal bureaucracies. Total number of bureaucrats and hiring/dismissal rates for bureaucratic staff over time. Disaggregated by department.'}
include_graphics(
  'plots/turnover_category.pdf'
)
```

@@

```{r, fig.cap= "Relative impact of bureaucratic turnover. Point estimates and confidence intervals retrieved from models with controls.", out.width = "210px"}
include_graphics(
  "plots/turnover_fit.pdf"
)
```

@@

```{r fig.cap = "Predicted and actual values for bureaucratic turnover. The line graph plots the predicted proportion of educational staff hired or firede. Circles' size is proportional to the number of observations contained in the data."}
include_graphics(
  "plots/plot_pred.pdf"
)
```

### 2020-07-06 presentation/presentation_job_market.tex
improve file naming

\begin{center}\includegraphics[width=240px]{figs/plot_global_1} \end{center}

@@

\begin{center}\includegraphics[width=240px]{figs/plot_global_2} \end{center}

@@

{\centering \includegraphics[width=180px]{figs/saeb_map}

@@

{\centering \includegraphics[width=230px]{figs/enrollment_dep}

@@

{\centering \includegraphics[width=230px]{figs/turnover_category}

@@

{\centering \includegraphics[width=210px]{figs/turnover_fit}

@@

{\centering \includegraphics[width=230px]{figs/plot_pred}

>>>>

\begin{center}\includegraphics[width=240px]{plots/plot_global_1} \end{center}

@@

\begin{center}\includegraphics[width=240px]{plots/plot_global_2} \end{center}

@@

{\centering \includegraphics[width=180px]{plots/saeb_map}

@@

{\centering \includegraphics[width=230px]{plots/enrollment_dep}

@@

{\centering \includegraphics[width=230px]{plots/turnover_category}

@@

{\centering \includegraphics[width=210px]{plots/turnover_fit}

@@

{\centering \includegraphics[width=230px]{plots/plot_pred}

### 2020-07-06 publication/paper_job_market.Rmd
improve file naming

```{r fig.cap = "Global enrollment rates and PISA test scores. Net enrollment rates calculated for primary education. PISA test scores based on a sample design."}
include_graphics(
  "figs/plot_global.pdf"
)
```

@@

```{r enrollment, fig.cap = "A decentralized system. Lower school education is primarily under the responsibility of municipalities, with important consequences for early cognitive development."}
include_graphics(
  "figs/enrollment_dep.pdf"
)
```

@@

```{r map, fig.cap="Uneven quality. Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores. Averages are weighted by participation rate."}
include_graphics(
  "figs/saeb_map.pdf"
) 
```

@@

```{r coalition, fig.cap = 'Empirical distribution of share of legislative seats in the mayoral coalition. The unit of analysis is the city council.'}
include_graphics(
  "figs/hist_coalition.pdf"
)
```

@@

\begin{figure}[H]
    \centering
    \includegraphics{figs/plot_pred}
    \caption{Predicted values for bureaucratic turnover. The graph plots the proportion of educational staff either hired or fired for any given year against the share of seats controlled by the executive. The circles' size is proportional to the number of observations contained at each value of the legislative share of seats.}
    \label{fig:turnover}
\end{figure}

@@

```{r}
include_graphics(
  "figs/balance_hlm.pdf"
)
```

@@

```{r}
include_graphics(
  "figs/balance_felm.pdf"
)
```

>>>>

```{r fig.cap = "Global enrollment rates and PISA test scores. Net enrollment rates calculated for primary education. PISA test scores based on a sample design."}
include_graphics(
  "plots/plot_global.pdf"
)
```

@@

```{r enrollment, fig.cap = "A decentralized system. Lower school education is primarily under the responsibility of municipalities, with important consequences for early cognitive development."}
include_graphics(
  "plots/enrollment_dep.pdf"
)
```

@@

```{r map, fig.cap="Uneven quality. Polygons represent municipalities, warmer colors indicate higher municipal average in standardized test scores. Averages are weighted by participation rate."}
include_graphics(
  "plots/saeb_map.pdf"
) 
```

@@

```{r coalition, fig.cap = 'Empirical distribution of share of legislative seats in the mayoral coalition. The unit of analysis is the city council.'}
include_graphics(
  "plots/hist_coalition.pdf"
)
```

@@

\begin{figure}[H]
    \centering
    \includegraphics{plots/plot_pred}
    \caption{Predicted values for bureaucratic turnover. The graph plots the proportion of educational staff either hired or fired for any given year against the share of seats controlled by the executive. The circles' size is proportional to the number of observations contained at each value of the legislative share of seats.}
    \label{fig:turnover}
\end{figure}

@@

```{r}
include_graphics(
  "plots/balance_hlm.pdf"
)
```

@@

```{r}
include_graphics(
  "plots/balance_felm.pdf"
)
```
